---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
p {font-style: italic;}

body {background-color: #e6f2ff}

h1, h2, h3 {font-family: 'Indie Flower'}
```

## Observing Patterns of Runners/Joggers by Weather Conditions and Time

This data set observes people and their activities during walks to Auckland University. The main focus for this analysis is looking at the variations of how the number of runners/joggers varies with weather conditions and time of day. 

```{r}
library(magick)
my_meme <- image_read("https://media.tenor.com/SVhrjuknABQAAAAM/run-chase.gif") %>%
  image_annotate(text = "RUNNING FROM RAIN!!!",
                 color = "#ffff00",
                 size = 20,
                 font = "Impact",
                 strokecolor = "#000000",
                 strokewidth = 1,
                 weight = 900,
                 gravity = "North")


frame1 <- my_meme %>%
  image_scale(250) %>%
  image_extent("500x500")

frame2 <- my_meme %>%
  image_scale(200) %>%
  image_extent("500x500")

frame3 <- my_meme %>%
  image_scale(150) %>%
  image_extent("500x500")

frame4 <- my_meme %>%
  image_scale(100) %>%
  image_extent("500x500")

frames <- c(frame1, frame2, frame3, frame4, frame3, frame2)

project2_meme <- image_animate(frames, fps = 20)

project2_meme

image_write(project2_meme, "project2_meme.gif")

```


```{r}
library(tidyverse)
logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vSk4t9n3EoJ_fMz-707n66U30B1gGBxweRcmUpLQSpgsF5ITTr7rKZLlL1imRWuIQS7oJYIIZcp3YpC/pub?gid=406574375&single=true&output=csv') 

latest_data <- logged_data %>%
  rename(
    timestamp = "Timestamp",
    num_running_jogging = "How many people did you notice running or jogging today?",
    main_activity = "What is the main type of activity of people you observed?",
    weather_conditions = "What was the weather like during your walk?",
    observation_time = "What time of the day did you make this observation?")
```
The maximum number of runners/joggers observed was `r max(latest_data$num_running_jogging)`. The minimum number of runners/joggers observed was `r min(latest_data$num_running_jogging)`.

Bar Chart 1: 

```{r}
#bar chart 1: Runners/Joggers by Weather Conditions
weather_split <- latest_data %>%
  separate_rows(weather_conditions, sep = ", ")

weather_split %>%
  ggplot() +
  geom_bar(aes(x = num_running_jogging, fill = weather_conditions)) +
  labs(title = "Number of Runners/Joggers by Weather Conditions",
       subtitle = "Comparing number of runners/joggers and weather conditions",
       x = "Number of Runners/Joggers",
       y = "Number of Observations",
       fill = "Weather")
```

Bar Chart 2

```{r}
#bar chart 2: Runners/Joggers by Time of Day
latest_data %>%
  ggplot() +
  geom_bar(aes(x = num_running_jogging, fill = observation_time)) +
  labs(title = "Number of Runners/Joggers by Time of Day",
       subtitle = "Comparing number of runners/joggers and time of day",
       x = "Number of Runners/Joggers",
       y = "Number of Observations",
       fill = "Time of Day")
```



